\setlength{\parskip}{10pt}

College life was one great roller coaster ride with all its ups and downs. I would like to thank the following for making it fun and bearable:

My VIP family: \textbf{Prince, Peter, Ate Mabelle, Ate Angelie, Ate Lau, Kuya Francis, Ate Che, Ate Meryll, Ate Alix, Ate Badette, Kuya Gino, Kuya Aaron, Kuya Elmer, Kuya Eric, Ate Phoebe, Ate Elexis, Micholo, Jeremy,} for all the progress reports, meetings, field works, and everything we have endured together. 

\textbf{Ate Mabelle} and \textbf{Ate Angelie}, whom I talk to most frequently about random things, thank you for your advices. \textbf{Ate Phoebe}, for being my buddy in our scuba diving class. \textbf{Prince}, thank you for helping me out in my experiments during the times you were in VIP. \textbf{Peter}, I included you in VIP family for you were once a part of it but you are also a friend whom I can count on to since high school. You may have chosen a different path in college but know that I will always support you in your endeavors.

\textbf{Ate Elexis} and \textbf{Kuya Elmer}, thank you for being the best ate and kuya to me. Thank you for constantly being there when I needed help the most and for selflessly giving out the best support you can give especially during my thesis days even until the defense day. Caring for others is a natural thing for both of you and I hope that stays within you. To \textbf{Ate Elexis}, for the VIP overnights. Even if we are like cats and dogs teasing each other all the time, I know that deep inside, you have a very good heart.

\textbf{UPPA family,} thank you for being a part of my college life. Thank you for giving me a home in my first three years in college through the several \textit{tambayans} we had. You have all helped me grow as an individual.

\textbf{IPL batchmates: Julia, Alfred, Damian, Pam, Tin, Shar, Pio,} thank you for all the shared moments during our third year and fourth year, when we were in charge of all entertainments and organizing all events for IPL, respectively. Kudos to us! We did it! 

\textbf{Julia} and \textbf{Alfred}, my VIP batchmates, thank you for the countless moments we have shared from R203 to R204 to outside the corners of NIP. Thank you for the all the good and bad (if there are) times and for the laughters. To \textbf{Julia}, thank you for always finding time to listen to my stories and for your inspiring unconditional love for the people you care for. To \textbf{Alfred}, thank you for the food treats and all the good times sharing jokes and stories. Thank you as well for sharing not just your love  for physics but for music through our jamming sessions with or without guitar.

\textbf{Pam} and \textbf{Tin}, my UP Village and IPL buddies, thank you for all the stories, fun times, and academic and research stresses we have shared. To \textbf{Tin}, thank you for our get-together with \textbf{Shua} and Damian and the fun online chats even in that one year that we were housemates and our rooms were just a few feet apart, our love for online chatting still prevailed. That or we are just two people too lazy to go out of our rooms. Nah, we just love online chatting (hehe). To \textbf{Pam}, although you never reply to my hundreds of text messages, okay fine, you replied once or twice, I know that you still care. Don't worry, we now understand that me-time is a must for you once in a while.

\textbf{Jess} and \textbf{Ariel}, my food trip buddies, thank your for never failing to go out on food trips with me, together with Tin, Pam, and Damian. Never have I thought that I would be ultimate friends with the two of you in my last year of college life. Just as birds of the same feather flock together, I strongly believe that our love for food has brought us closer. \textit{Ika nga, ``Okay lang gumastos, basta sa pagkain."}

\textbf{Damian} and \textbf{Josh}, our batch is forever indebted to the two of you. Thank you for sharing all your physics, math, and computer-related skills and knowledge to us, from the very first year of college life down to the last. To \textbf{Josh}, as one who shares the same faith as mine, thank you for all our conversations which most of the time, if not always, end up in praying for one another. To \textbf{Damian}, thank you for the untiring and unfailing support you give. Thank you for always having an answer to all my academic-, research-, and even life-related questions. Thank you as well for all the corny times, honestly dude, they are the best.

To the rest of my batchmates, \textbf{Aiko, Meryll, Shami, Tom, Xavier, King, Nove, Nicole,} thank you as well for all the fun times and shared moments. Can't imagine college life without you guys. 

To those who I forgot to mention but have helped me in one way or another during my stay in college, specially in the completion of my thesis, thank you so much.

\textbf{Dr.\ Maricor Soriano}, my sincerest gratitude goes to you. Thank you for the enduring patience and for selflessly sharing your knowledge and expertise in Physics, specially in image processing. A page of this thesis is not enough if I really am to put into words and write down my gratefulness for having you as my adviser. Your love for science, not just for the sake of discovering new things, but science which you can share to the public is truly exceptional and is the ultimate thing I admire about you. 

My parents, \textbf{Ronald} and \textbf{Ruth Aguilar}, for being the best parents one can possibly have. Thank you for all the love and support - may it be moral, financial, or spiritual, and for always letting me follow my dreams. Thank you for never ceasing to pray for me. Never have I felt unloved by both of you even though we are miles apart from each other. My older brother, \textbf{Renz Aguilar}, for being protective of me and for all the times you were there when I needed help.

To the \textbf{Lord God Almighty}, all the praises, honor, and glory, I give them back to You. I am nothing without You.

%Dr.\ Ronald Banzon for the abiding jollity.

%Dr.\ Arnel Salvador, Dr.\ Armando Somintac and Dr.\ Eric Galapon for the generosity in imparting their expertise.

%The Philippine Council for Advanced Science and Technology Research and Development for the two-year financial support. The High Performance Computing Facility of the Computational Science Research Center for the permission to tap their computers.

%The Structure and Dynamics Group specially this semester's graduating students: Ms.\ Criswelynn Castro, Ms.\ Kristine Eia Antonio, Ms.\ Micielle Capili, and Ms.\ Mariel Rodriguez for remaining until the completion of our theses.

%The Papuri sa Dyos cell of the Higher Rock Christian Church specially to Ms.\ Maybelle Ninon for the persevering prayers end encouragements.

%My friends specially in the graduate school: Ms.\ Elise Stacey Agra, Ms.\ Gendith Sardane, Ms.\ Kristine Manibog, and Ms.\ Josephine Garcia for the good times. To Ms.\ Louella Judy Vasquez for the previous advices.

%Ms.\ Cyril Sadia for the unrelenting efforts in assisting and interceding.
%
%The LORD Jesus Christ who extravagantly gave all of the mentioned and unmentioned graces.